Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-17 paper_knowledge.tex
Commented out the anecdote on light detection error (naming experiment)
This to address reviewer 3 comment and shorter the paper

An unexpected example of what the symbolic reasoning layer brings to more
traditional robotic architectures emerged during the \emph{Naming} experiment:
the perception routines provided segmented blobs corresponding to objects along
with their colors to update the information in ORO. At some point, ORO suddenly
refused to add an object. What seemed at first a communication bug between
modules, was actually the consequence of a consistency check by ORO: because of
bad light conditions, the color recognition was not very reliable, and the same
object was set to have two different colors at the same time. Since the
\concept{hasColor} predicate we had decided to use was a functional predicate
(\ie objects can have only one color), ORO inferred an inconsistency and
discarded the new fact. This kind of logical failure can be used to improve
low-level perception outcomes by ``closing the loop'' with high-level, symbolic
knowledge.

>>>>

% An unexpected example of what the symbolic reasoning layer brings to more
% traditional robotic architectures emerged during the \emph{Naming} experiment:
% the perception routines provided segmented blobs corresponding to objects along
% with their colors to update the information in ORO. At some point, ORO suddenly
% refused to add an object. What seemed at first a communication bug between
% modules, was actually the consequence of a consistency check by ORO: because of
% bad light conditions, the color recognition was not very reliable, and the same
% object was set to have two different colors at the same time. Since the
% \concept{hasColor} predicate we had decided to use was a functional predicate
% (\ie objects can have only one color), ORO inferred an inconsistency and
% discarded the new fact. This kind of logical failure can be used to improve
% low-level perception outcomes by ``closing the loop'' with high-level, symbolic
% knowledge.
